---
title: "WEEK2 - ASSIGNMENT"
author: "G OLIVEIRA"
format: html
editor: visual
---

### **Exercises**

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
```

```{r}
data(mpg)
```

1.  What happens if you facet on a continuous variable?

```{r}
ggplot(mpg, aes (x = hwy, y = displ)) + geom_point(fill = "pink", shape = 24)
```

2.  Why did the following code not result in a plot with blue points?

```{r}
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy, color = "blue"))
```

A: the color does not work because when putting inside aes, the comand works like a legend to the graph

3.  What does the `stroke` aesthetic do? What shapes does it work with? (Hint: use [`?geom_point`](https://ggplot2.tidyverse.org/reference/geom_point.html))

```{r}
? geom_point
```

A: "The stroke aesthetic to modify the width of the border"

4.  What happens if you map an aesthetic to something other than a variable name, like `aes(color = displ < 5)`? Note, you’ll also need to specify x and y.

```{r}
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy, color = displ < 5))
```

A: it divides in two categories the variable displ: True for \< 5 and False for \> 5. and it displays in two separated colors.
